---
title: "Prediction Challenge 1"
author: "Valerie Le"
date: "2023-04-16"
output: html_document
---

**Data load**
```{r}
hire <- read.csv("C:/Users/lpnhu/Downloads/HireTrainApr10.csv")
```

**Data exploration**
```{r}
nrow(hire)
colnames(hire)
unique(hire$Coding)
unique(hire$Impression)
unique(hire$Major)
unique(hire$College)
unique(hire$Hired)
```
**Use chi-squared test to test each variable relationship to the predicted column (hired)**
In sum, candidates' _major_ influences whether they get hired or not. Hence, _major_ would less likely to play a role in prediction model.
```{r}
#H01: Candidates' coding skill is independent of whether they get hired or not
#Ha1: Candidates's coding skill influences whether they get hired
chisq.test(hire$Hired,hire$Coding)
#H02: Candidates' first impression is independent of whether they get hired or not
#Ha2: Candidates's impression influences whether they get hired
chisq.test(hire$Hired,hire$Impression)
#H03: Candidates' major is independent of whether they get hired or not
#Ha3: Candiates's major influences whether they get hired
chisq.test(hire$Hired,hire$Major)
#H04: Candiates'college is independent of whether they get hired or not
#H02: Candidates's college influences whether they get hired
chisq.test(hire$Hired,hire$College)
```
**Use table() for subsets of the HireTrain data set. Find such subsets which are "decisive" either with vrery large proportion of Hired = 'Yes' or with very high proportion of Hired = 'No'**

```{r}
table(hire$Hired)
table(hire[hire$Coding=='Excellent',]$Hired)
#Excellent and nerdy seems to be a great patternt to get hired
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy',]$Hired)
```

IT+ nerdy+ any school except BestCollege coding skills seem to be a decisive pattern.
```{r}
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Nerdy'& hire$College=='Peters',]$Hired)
```
Excellent+ Outgoing+ any school except BestCollege coding skills seem to be a decisive pattern.
```{r}
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Outgoing'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Outgoing'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Outgoing'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Outgoing'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Outgoing'& hire$College=='Peters',]$Hired)
```
Excellent + Confident + any major seems to be the pattern for hiring
```{r}
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Confident'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Confident'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Confident'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Confident'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Confident'& hire$College=='Peters',]$Hired)
```
Excellent + Shy + any major seems to be the pattern for hiring. Moreover, Data Sciences and Stats major have 100% chance of hiring

```{r}
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Shy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Shy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Shy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Shy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Excellent' & hire$Impression== 'Shy'& hire$College=='Peters',]$Hired)
```
_Testing Coding skill = Weak_
```{r}
table(hire[hire$Coding=='Weak',]$Hired)
```
Weak coding skill + Nerdy  seems to get REJECTED. 
```{r}
table(hire[hire$Coding=='Weak' & hire$Impression== 'Nerdy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Nerdy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Nerdy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Nerdy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Nerdy'& hire$College=='Peters',]$Hired)
```
Weak + Outgoing + any major seems to be the pattern for NOT hiring!!
```{r}
table(hire[hire$Coding=='Weak' & hire$Impression== 'Outgoing'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Outgoing'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Outgoing'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Outgoing'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Outgoing'& hire$College=='Peters',]$Hired)
```
Weak + Confident + any major seems to be the pattern for NOT hiring!!
```{r}
table(hire[hire$Coding=='Weak' & hire$Impression== 'Confident'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Confident'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Confident'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Confident'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Confident'& hire$College=='Peters',]$Hired)
```

Weak + Shy + any major seems to be the pattern for NOT hiring. 

```{r}
table(hire[hire$Coding=='Weak' & hire$Impression== 'Shy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Shy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Shy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Shy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='Weak' & hire$Impression== 'Shy'& hire$College=='Peters',]$Hired)
```

_Testing Coding skill = OK_
```{r}
table(hire[hire$Coding=='OK',]$Hired)
```
OK coding skill + Nerdy + Best College has 100% chance of getting rejected

```{r}
table(hire[hire$Coding=='OK' & hire$Impression== 'Nerdy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Nerdy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Nerdy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Nerdy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Nerdy'& hire$College=='Peters',]$Hired)
```
OK + Outgoing + any major seems to be the pattern for hiring!!
```{r}
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='Peters',]$Hired)
```
OK + Confident + any major seems to be the pattern for hiring!!
```{r}
table(hire[hire$Coding=='OK' & hire$Impression== 'Confident'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Confident'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Outgoing'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Confident'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Confident'& hire$College=='Peters',]$Hired)
```

OK + Shy + Best College have 100% chance of getting REJECTED

```{r}
table(hire[hire$Coding=='OK' & hire$Impression== 'Shy'& hire$College=='Redbrick',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Shy'& hire$College=='PJIT',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Shy'& hire$College=='BYU',]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Shy'& hire$College=='BestCollege' ,]$Hired)
table(hire[hire$Coding=='OK' & hire$Impression== 'Shy'& hire$College=='Peters',]$Hired)
```

**Prediction Model**
excellent + nerdy + bestcollege doesn't have an obvious pattern
```{r}
myprediction <- hire1
decision <-rep('No',nrow(myprediction))

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' & myprediction$TwitterFOLLOWERS <62] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' & myprediction$TwitterFOLLOWERS >9243] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' & myprediction$TwitterFOLLOWING <442] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' &  myprediction$TwitterFOLLOWING >9878] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' & myprediction$TikTokFOLLOWERS >9731] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BYU' & myprediction$TikTokFOLLOWING <295] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' &   myprediction$TwitterFOLLOWERS >8558] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' & myprediction$TwitterFOLLOWING <563] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' &  myprediction$TwitterFOLLOWING >9607] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' &   myprediction$TikTokFOLLOWERS < 277] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' &     myprediction$TikTokFOLLOWERS > 9529] <- 'Yes'


decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWING <524] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWING > 9621] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' &   myprediction$TwitterFOLLOWERS < 179] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' & myprediction$TwitterFOLLOWING <141] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' &  myprediction$TwitterFOLLOWING >9062] <- 'Yes'


decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' &     myprediction$TikTokFOLLOWERS > 8663] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' & myprediction$TikTokFOLLOWING <133] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'PJIT' & myprediction$TikTokFOLLOWING > 9744] <- 'Yes'


decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BestCollege' &   myprediction$TwitterFOLLOWERS > 9140] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BestCollege' & myprediction$TwitterFOLLOWING <225] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BestCollege' & myprediction$TwitterFOLLOWING >9696] <- 'Yes'


decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BestCollege' &     myprediction$TikTokFOLLOWERS > 7883] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'BestCollege' & myprediction$TikTokFOLLOWING <1672] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Redbrick' & myprediction$TwitterFOLLOWING <1467] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Redbrick' & myprediction$TwitterFOLLOWING >9855] <- 'Yes'


decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Redbrick' &     myprediction$TikTokFOLLOWERS > 6650] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWING <250] <- 'Yes'

decision[myprediction$Coding == 'Excellent' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWING >9772] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'BYU' &   myprediction$TwitterFOLLOWERS >9674] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'BYU' & myprediction$TwitterFOLLOWING <1523] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'BYU' & myprediction$TwitterFOLLOWING >9757] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'BYU' & myprediction$TikTokFOLLOWERS >9828 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'BYU' & myprediction$TikTokFOLLOWING <9398 ] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' &   myprediction$TwitterFOLLOWERS >9621] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' &   myprediction$TwitterFOLLOWERS <232] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' & myprediction$TwitterFOLLOWING <393 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' & myprediction$TwitterFOLLOWING >8384 ] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWERS >9156 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWING <150  ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWING >9836   ] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'PJIT' &   myprediction$TwitterFOLLOWERS <443] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'PJIT' &   myprediction$TwitterFOLLOWERS >9167] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'PJIT' & myprediction$TwitterFOLLOWING <511 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'PJIT' & myprediction$TikTokFOLLOWERS >7436 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'BestCollege' &   myprediction$TwitterFOLLOWERS >9687] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'BestCollege' & myprediction$TwitterFOLLOWING >9844 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' &      myprediction$TwitterFOLLOWERS >9029] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' & myprediction$TwitterFOLLOWING <719 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' &  myprediction$TwitterFOLLOWING >9626 ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWERS <341] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWERS >5721] <- 'Yes'


decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWING <669  ] <- 'Yes'

decision[myprediction$Coding == 'OK' & myprediction$College == 'Redbrick' & myprediction$TikTokFOLLOWING >9384   ] <- 'Yes'


decision[myprediction$Coding == 'Weak' & myprediction$College == 'BYU' &  myprediction$TwitterFOLLOWERS >9577] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'Peters' &      myprediction$TwitterFOLLOWERS >8882 ] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWERS >7610 ] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'Peters' & myprediction$TikTokFOLLOWING >9916    ] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'PJIT' &   myprediction$TwitterFOLLOWERS >9400] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'PJIT' & myprediction$TwitterFOLLOWING <519] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'PJIT' &     myprediction$TikTokFOLLOWERS <91] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'PJIT' & myprediction$TikTokFOLLOWING <262] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'BestCollege' &   myprediction$TwitterFOLLOWERS >9409] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'BestCollege' & myprediction$TwitterFOLLOWING >9975] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'BestCollege' &     myprediction$TikTokFOLLOWERS >9535 ] <- 'Yes'

decision[myprediction$Coding == 'Weak' & myprediction$College == 'BestCollege' & myprediction$TikTokFOLLOWING <372] <- 'Yes'


#Coding Skill is Excellent
decision[myprediction$Coding=='Excellent'] <- 'Yes'
#Coding skill is OK
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Peters'] <- 'Yes'


decision[myprediction$Coding=='OK' & myprediction$Impression== 'Outgoing'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Confident'] <- 'Yes'

decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Peters'] <- 'Yes'

#Coding Skill is Weak
decision[myprediction$Coding=='Weak' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'

myprediction$Hired <- decision
error <- mean(hire1$Hired!= myprediction$Hired)
error
```
**One-step crossvalidation**
```{r}
v<-sample(1:nrow(hire))
v[1:5]
hireScrambled<-hire[v, ]
#one step cross-validation
hireSample<-hireScrambled[nrow(hireScrambled)-10:nrow(hireScrambled), ]
myprediction<-hireSample
decision <-rep('No',nrow(myprediction))

#Coding Skill is Excellent
decision[myprediction$Coding=='Excellent'] <- 'Yes'
#Coding skill is OK
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Peters'] <- 'Yes'


decision[myprediction$Coding=='OK' & myprediction$Impression== 'Outgoing'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Confident'] <- 'Yes'

decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Peters'] <- 'Yes'

#Coding Skill is Weak
decision[myprediction$Coding=='Weak' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'

myprediction$Hired <- decision
error <- mean(hireSample$Hired!= myprediction$Hired)
error

#scramble the hire frame
v<-sample(1:nrow(hire))
v[1:5]
hireScrambled<-hire[v, ]
#one step crossvalidation
hireSample<-hireScrambled[nrow(hireScrambled)-10:nrow(hireScrambled), ]
myprediction<-hireSample
decision <-rep('No',nrow(myprediction))
#Coding Skill is Excellent
decision[myprediction$Coding=='Excellent'] <- 'Yes'
#Coding skill is OK
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Peters'] <- 'Yes'

decision[myprediction$Coding=='OK' & myprediction$Impression== 'Outgoing'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Confident'] <- 'Yes'
 
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Peters'] <- 'Yes'
 
#Coding Skill is Weak
decision[myprediction$Coding=='Weak' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'



myprediction$Hired <- decision
error <- mean(hireSample$Hired!= myprediction$Hired)
error
```
**ADDITIONALLY**
_Getting to know the data_
```{r}
colnames(hire)
summary(hire)
unique(hire$Coding)
nrow(hire)
unique(hire$Major)
unique(hire$College)
table(hire$Coding)
table(hire$Major)
table(hire$Impression)
table(hire$College)
```

Did you know that students who comes from RedBrick are more outgoing than students from other schools?

```{r}
table(hire$College,hire$Impression)
```

Did you know that students who are confident have ~64% of getting hired?
```{r}
table(hire$Impression,hire$Hired)
```

What are the odds that students have weak coding skills from Best College get hired?

[ANS]: Posterior odds = 0.2856
Likelihood ratio = .17
Prior Odds = 1.68
```{r}
#Belief: Candidate get hired
#Observation: Weak coding skills
Prior<-nrow(hire[hire$Hired =='Yes',])/nrow(hire)
Prior
PriorOdds<-round(Prior/(1-Prior),2)
PriorOdds
TruePositive<-round(nrow(hire[hire$Hired=='Yes'& hire$Coding=='Weak'& hire$College== 'BestCollege',])/nrow(hire[hire$Coding=='Weak',]),2)
TruePositive
FalsePositive<-round(nrow(hire[hire$Hired!='Yes'& hire$Coding=='Weak' &hire$College =='BestCollege',])/nrow(hire[hire$Hired!='Weak',]),2)
FalsePositive
LikelihoodRatio<-round(TruePositive/FalsePositive,2)
LikelihoodRatio
PosteriorOdds <-LikelihoodRatio * PriorOdds
PosteriorOdds
Posterior <-PosteriorOdds/(1+PosteriorOdds)
Posterior
```

**Preparing submission.csv for Kaggle**
```{r}
test <- read.csv("C:/Users/lpnhu/Downloads/test_challenge1.csv")
submission <- read.csv("C:/Users/lpnhu/Downloads/sample_submission_challenge1.csv")

myprediction <- test
decision <-rep('No',nrow(myprediction))

#Coding Skill is Excellent
decision[myprediction$Coding=='Excellent'] <- 'Yes'
#Coding skill is OK
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Nerdy' & myprediction$College=='Peters'] <- 'Yes'


decision[myprediction$Coding=='OK' & myprediction$Impression== 'Outgoing'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Confident'] <- 'Yes'

decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Redbrick'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='PJIT'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='BYU'] <- 'Yes'
decision[myprediction$Coding=='OK' & myprediction$Impression== 'Shy' & myprediction$College=='Peters'] <- 'Yes'

#Coding Skill is Weak
decision[myprediction$Coding=='Weak' & myprediction$Impression== 'Nerdy' & myprediction$College=='Redbrick'] <- 'Yes'

submission$Prediction <- decision
write.csv(submission,'mysubmission1.csv',row.names = FALSE)
```